\section{Related Work}
Fallahi et. al. \cite{Fallahi2016} implemented automatic rule generation for the SIDS Snort. They used two data mining algorithms called Ripper and C5.0. They investigated five types of attacks and tested it on the ISCX 2012 dataset. Rather than looking to individual packets, they looked at the flow of data. From the flow 17 features were selected to generate rules. Fallahi et. al. applied this approach to a single dataset which contained various attacks, rather than focusing on DoS attacks. 

Fouda \cite{Fouda2017} proposes a payload based signature generation specific for DDoS attacks. Various pattern matching algorithms are tested to find the amount of similarity between incoming traffic and traffic that is associated with a DDoS attack. It was found that Smith-Waterman and Longest Common Substring algorithms yielded the highest accuracy. A problem apparent in this approach is that it tends to become slow. In 2003 IDSs could only cope with up to 200 Mbps of traffic \cite{Lai2004}. 

Chimetseren et. al \cite{Chimetseren2014} proposes signature based generation method using Discrete Fourier Transform. In this method the payload between client and server are regarded as discrete waveform. They create a spectrum for normal, known attack and unknown attack sessions.  This approach is tested on the Kyoto2006+ dataset\footnote{\url{http://www.takakura.com/Kyoto_data/}}. By also generating a spectrum for normal sessions, they are able to detect unknown attacks. However, this does yield a 5\% false positive in the selected dataset.  

