% You should not remove this section
\section{Conclusion}
\label{section:conclusion}
In this paper we try to show whether Bro is a suitable IDS which is capable of detecting attacks with automated generated rules based on the signatures retrieved from DDoSDB. We tried to show this by building a test setup that resembles a common internet setup. In this setup we replayed various attack vectors to a target machine which port was mirrored to a machine running the Bro IDS. 

From this we can conclude that (1) it is possible to automatically generate Bro signature rules based on signatures received from DDoSDB, (2) generation time of the signature rules is based on the number of fields the signature has and (3) Bro's response time does not increase dramatically when more signatures are added. 

For future work one could look at the Bro scripting language. The Bro scripting language allows for more detailed analisys of packets. Also one could increase the number of signatures to discover the limit of signatures the Bro IDS can handle. Furthermore, it would also be nice to see how the generated rules behave in terms of accuracy (false positives and false negatives). 

\section{Acknowledgements}
We would like to thank Jair Santanna for his valuable feedback, supplying the tools needed for the test setup and enabling us to gain access to the data stored in DDoSDB. Furthermore, We would like to thank Vincent Dunning for aiding in the process of creating the test setup and carrying out the experiments.  